A robust and memory-efficient transition state search method for complex energy landscapes

### 2022-08-22 manuscript.tex
Added CINEB to table

% Table
\usepackage{multirow}

@@

\subsection{Comparison with chain-of-states methods}
\begin{figure}[tb]
  \includegraphics{testsystems.pdf}
  \caption{\label{fig:testsystems}
    The three systems used for comparison with chain-of-states methods.
    These are: (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
    The configurations shown correspond to the two minimum energy states and the transition state, marked by an asterisk.
  }
\end{figure}

@@

\begin{table}[ht]
  \begin{ruledtabular}
  \begin{tabular}{ccccccc}
    \multirow{2}{*}{System} & \multirow{2}{*}{BITSS} &
    \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}BITSS-\\HEVF\end{tabular}} &
    \multicolumn{4}{c}{DNEB-HEVF} \\
             &             &             & 3           & 5           & 10          & 20          \\
    \hline
    LJ-7     & 148         & 144         & 135         & 138         & 208         & 361         \\
    Buckling & \num{12866} & \num{14446} & ---         & \num{7315}  & \num{6242}  & \num{12094} \\
    Wetting  & \num{12100} & \num{17262} & \num{17840} & \num{17721} & \num{20221} & \num{48286} \\
  \end{tabular}
  \end{ruledtabular}
  \caption{\label{tab:speed}
    Number of potential gradient calculations required to reach the transition state for the three comparison examples.
    The approach combining DNEB and hybrid eigenvector-following (HEVF) has been run for different numbers of images.
    Convergence is determined as when the root-mean-square of the gradient is less than $10^{-4}$.
  }
\end{table}

>>>>

% Table
\usepackage{multirow}
\usepackage{booktabs}
\newcommand{\tworow}[1]{\multirow{2}{*}[-0.5\dimexpr \aboverulesep + \belowrulesep + \cmidrulewidth]{#1}}

@@

\subsection{Comparison with chain-of-states methods}
\begin{figure}[htb]
  \includegraphics{testsystems.pdf}
  \caption{\label{fig:testsystems}
    The three systems used for comparison with chain-of-states methods.
    These are: (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
    The configurations shown correspond to the two minimum energy states and the transition state, marked by an asterisk.
  }
\end{figure}

@@

\begin{table*}[tb]
  \begin{ruledtabular}
  \begin{tabular}{c cc cccc cccc}
    \tworow{System} & \tworow{BITSS} &
      \tworow{\begin{tabular}[c]{@{}c@{}}BITSS-\\HEVF\end{tabular}} &
      \multicolumn{4}{c}{DNEB-HEVF} & \multicolumn{4}{c}{CINEB} \\
    \cmidrule(lr){4-7}\cmidrule(lr){8-11}
             &             &             & 3           & 5           & 10          & 20          & 3   & 5          & 10          & 20          \\
    \hline
    LJ-7     & 148         & 144         & 135         & 138         & 208         & 361         & 30  & 153        & 2000        & 1692        \\
    Buckling & \num{12866} & \num{14446} & ---         & \num{7315}  & \num{6242}  & \num{12094} & --- & \num{8352} & \num{19360} & \num{77904} \\
    Wetting  & \num{12100} & \num{17262} & \num{17840} & \num{17721} & \num{20221} & \num{48286} & --- & ---        & ---         & ---         \\
  \end{tabular}
  \end{ruledtabular}
  \caption{\label{tab:speed}
    Number of potential gradient calculations required to reach the transition state for the three comparison examples.
    The climbing-image nudged-elastic-band (CINEB) and DNEB with hybrid eigenvector-following (HEVF) methods have been run for different numbers of images.
    Convergence is determined to be when the root-mean-square of the gradient at the estimate for the transition state is less than $10^{-4}$.
    The fields left blank indicate that the method has not converged to the correct transition state.
  }
\end{table*}
